---
title: "StackedBar_Flex24"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    runtime: shiny
---

```{r setup, include=FALSE}

rm(list=ls())
### NOTES
# Converted all tibbles to data frames to get rid of phantom column name errors

### NAMING RULES
# Functions: FuncTest(dat1_there, dat2_here)
# Action buttons: button_PushMe
# User inputs: sel_SelectMe
# Lists, data frames, vectors, variables...: station_files_list, station_df,  station_vec, here_is_a_variable
# Data frame cols: df$ColThisOne, df$ColThatOne
# List elements: list$ElementOne, list$ElementTwo
# Reactive elements: rv$ThisOne, rv$ThatOne
# Temporary variables: temp_this_df
# Well panel id's: wp_FilterParkSite

#options(url.method = "wininet")
#options(repos="http://cran.revolutionanalytics.com")
#options(repos = c(CRAN = "https://cloud.r-project.org"))

### Load libraries -----
# Will automatically install any libraries it can't find
pkgs <- c("flexdashboard", 
              "shiny", 
              "knitr", 
              "odbc", # pull data from SQL server
              "leaflet", 
              "here",
              "plotly", 
              "tidyverse", 
              "plyr", 
              "sf",
              "readr",
              "magrittr",
              "bslib", 
              "ggplot2",
              "patchwork",
              "leaflet.extras", 
              "lubridate",
              "forcats",
              "httr", # use web services
              "rgdal", # to use readOGR
              "sp", # transform projections
              "purrr", # for applying functions to dplyr groups
              "dataMaid", # for data checks
              "shinyFiles", # for user to save files in specified location
              "RColorBrewer", # to display brewer palettes
              "shinyjs", # for easy functions that use JavaScript
              "stringr", # to detect text snippets
              "reactable",
              "reactablefmtr",
              "base", 
              "htmltools", 
              "ggthemes",
              "data.table", # for fast lag calcs
              "DT", # for interactive tables
              "cowplot", # to get legends from plots
              "crosstalk", # for SharedData
              "gridExtra", # for arranging plots and adding plot annotations (ggplotly can't do captions or subtitles)
              "RgoogleMaps", # for MaxZoom & MinZoom
              "leaflet.minicharts") # for pie charts in leaflet maps


installed_pkgs <- pkgs %in% installed.packages()
if (length(pkgs[!installed_pkgs]) > 0) install.packages(pkgs[!installed_pkgs],dep=TRUE, repos='http://cran.us.r-project.org') #repos is new line of code!!!! 
lapply(pkgs, library, character.only = TRUE)

invisible(lapply(pkgs, library, character.only = TRUE))

options(shiny.maxRequestSize=60*1024^2) #increase the file upload limit to 90MB.

rv <- reactiveValues(SeedlingSapling = NULL, SpeciesDiversity = NULL, Tree = NULL, CanopyCover = NULL, StandHeight = NULL, Genus = NULL, LatLong = NULL, Species_Cover = NULL, Cover_Class = NULL, Exotics = NULL, CWD = NULL, BroadGroup = NULL, CycleNumber = NULL)


#### might have to change the reactive value names??? read the shiny
temp_rv <- shiny::reactiveValues(
  plotly_tree = NULL, 
  # df_treefull = NULL, 
  col_sptreefull = NULL
)
```

```{r}
#reading in csvs

trees <- read_csv(here::here("output", "CUPN_TreeBasics.csv")) #NEWNEW cycle tree basics
seedlingsapling <- read_csv(here::here("output", "CUPN_SeedlingSapling.csv")) #NEWNEW cycle seedling sapling
broadgroup <- read_csv(here::here("output", "CUPN_BroadGroup.csv")) #used to be broadgroup
# species_rich <- read_csv(here::here("Data_In","SpeciesDiversity_LongFormat_20230421.csv")) #waiting on new data from Tim
genus <- read_csv(here::here("output", "TaxaTable.csv"))
location <- read_csv(here::here("output", "Location_Table2.csv")) #let's just call this LOCATION
genus_group <- read_csv(here::here("output", "Genus_grouping.csv"))
events <- read_csv(here::here("output", "CUPN_EventTable2.csv"))

```


```{r functions}
### Functions-----

#rounding function 
#stick to a certain function naming rule
round_df <- function(x, digits) {
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

options(scipen=999)

#keeping only first letter of character
makeInitials <- function(charVec) {
  make.unique(vapply(strsplit(toupper(charVec), " "), 
                     function(x) paste(substr(x, 1, 1), collapse = ""), 
                     vector("character", 1L)))
}

#color palettes
Okabe_Ito <- c("#E69F00", "#56B4E9", "#009E73", '#CC6677',"#F0E442", "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",'#DDDDDD', '#EE6678', '#99DDFF', 
               '#BBCC33', '#332288', '#882255', '#FFAABB')

okabe_ito <- c( "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",  '#CC6677', '#BBCC33', '#99DDFF', 
                '#332288', '#882255', '#FFAABB', "#E69F00", "#56B4E9", "#009E73", "#F0E442")

viridis <- c("#fde725", "#5ec962", "#21918c","#3b528b","#440154")

jane <- c('#a5cee2', '#1f78b4', '#b2df8a', '#e7298b', '#33a02b', '#997dd4', '#fc9a99','#e21a1c', '#fdbe6f', '#ff7f00', '#9c9c9c', '#cab2d6', '#6a3d9a', '#feff99', '#b15929')

# function to group by a plot, year and find the count of n
makefun <- function(data) {
  data %>% 
  dplyr::group_by(Plot_Code, Year) %>%
  dplyr::summarize(n())
  
}
##### css functions
integer_columns <- function(maxWidth = 60, ...) {
  colDef(maxWidth = maxWidth, align = "center",...)
}

with_tooltip <- function(value, tooltip) {
  tags$abbr(style = "text-decoration: underline; text-decoration-style: dotted; cursor: help", title = tooltip, value)
}

# lists for organizing column orders
positions <- c("Tree", "Sapling", "Seedling")

col_group <- c("Plot_Code", "Plant_Code", "Start_Date", "Sample_Year", "Event_ID")

#Neesd to get ride of Network, Park, and Subunit, Change Start_Date to Sample Date?
common_columns <- c("Network_Code", "Park_Code", "Subunit_Code", "Plot_Code", "Start_Date", "Event_Type_Name", "Year") 
remove_habcolumns <- c("Fit", "Confidence", "Sample_Year", "Event_ID", "Start_Date", "Plot_Code") 
```

```{r}
func_processdata <- function(df, growth_form) {
  df %>%
    dplyr::mutate(Start_Date = as.Date(lubridate::mdy_hm(Start_Date)),
                  Sample_Year = as.factor(Sample_Year),
                  Growth_Form = growth_form)
}

df_genus <- genus %>% 
  dplyr::select(Plant_Code, Genus) 

df_events <- func_processdata(events, NA)

# df_events %<>%
#   dplyr::mutate(Subunit_Code = substr(Plot_Code, 1, 4))

df_trees <- func_processdata(trees, "Tree") %>%
  dplyr::filter(Status_Name == "Live Tree") %>%
  dplyr::mutate(BA_ha = ((pi * DBH^2) / 40000) / 0.04)          # df_trees and df_seedsap are slaying

df_seedsap <- func_processdata(seedlingsapling, NA)

broadgroup <- func_processdata(broadgroup, NA)


 # new code for woody map _flex24
location %<>%
    dplyr::select(Network_Code, Park_Code, Subunit_Code, Plot_Code, Latitude, Longitude)

genus_grouping <-  if (!exists("genus_group")) {
  genus_grouping <- NULL
  } else { 
  genus_grouping <- genus_group
  }

```

```{r}
df_sap <- df_seedsap %>%
    dplyr::select(all_of(col_group), 
                  Plant_Code,
                  Sapling_Total) %>%
    dplyr::group_by(across(all_of(col_group))) %>%
    dplyr::summarize(Sapling = sum(Sapling_Total))
  
  df_seed <- df_seedsap %>%
    dplyr::select(all_of(col_group), 
                  Plant_Code, 
                  Seedling_Total) %>%
    dplyr::group_by(across(all_of(col_group))) %>%
    dplyr::summarize(Seedling = sum(Seedling_Total))
  
  df_treesp <- df_trees %>%
    dplyr::group_by(Plot_Code, Start_Date, Event_ID, Sample_Year, Plant_Code) %>%
    dplyr::summarise(Tree = n())
  # 7452 from 21715
  
    df_treefull <- Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list(df_sap,
                                df_seed,
                                df_treesp))
    
    df_treefull %<>%
      tidyr::pivot_longer(cols = c(Seedling, Sapling, Tree), 
               names_to = "Strata", 
               values_to = "Count")
    
    
```

```{r}
all_events <- df_events %>%
  left_join(broadgroup) %>%
  dplyr::filter(Event_Type != "QA/QC")%>% 
  left_join(location %>% dplyr::select(Network_Code, Park_Code, Subunit_Code, Plot_Code), by = "Plot_Code")

```

```{r}
# input <- list()
# input$stack_spatialunit <- "Subunit_Code"
# input$stack_userunit <- "BIRT"
# input$stack_season <- "Sample_Year"
# input$stack_year <- "2011"
# input$stack_spatialhabitat <- "All"
# input$stack_userhabitat <- "All" #Appalachian & Interior Mesophytic Forest"
# input$stack_spgroup <- "Genus" # options are Genus and plant code
# input$stack_usergroup <- "Genus" #group x, y, z
observeEvent(eventExpr = input$button_UpdatePlots, {
  
  cat("Line0")

 shiny::req(!is.null(input$stack_spatialunit), !is.null(input$stack_userunit), !is.null(input$stack_spatialhabitat), !is.null(df_treefull), !is.null(all_events), !is.null(input$stack_year), !is.null(input$stack_spgroup), !is.null(input$stack_season), !is.null(input$stack_userhabitat))

#this code is selecting for the spatial scale, for plotting bar chats we can either look at everything across the entire plot, ORRRR  we can look within a park/subunit and select for the smaller grouping
 if (input$stack_spatialhabitat == "All" & input$stack_userhabitat == "All") {
   nplot <- all_events %>%
     dplyr::filter(!!as.name(input$stack_spatialunit) == input$stack_userunit) %>%
     distinct(!!as.name(input$stack_season), Plot_Code, Event_ID)
   
   } else {
   nplot <- all_events %>%
     dplyr::filter(!!as.name(input$stack_spatialunit) == input$stack_userunit) %>%
     dplyr::filter(!!as.name(input$stack_spatialhabitat) == input$stack_userhabitat) %>%
     distinct(!!as.name(input$stack_season), Plot_Code, Event_ID)
   } 

stack_sequence <- nplot %>%
  dplyr::filter(!!as.name(input$stack_season) == input$stack_year) %>%
  pull(Event_ID)


#this code is selecting for if there is a different type of SPECIES GROUPING that we want either GENUS (top 8) or by another grouping based on species and a higher group

# woodystacktop_species <- 
if (input$stack_spgroup == "Genus" & input$stack_usergroup == "Genus") {

df_stacktop <- df_trees %>% # used to be df_treefull
  dplyr::filter(Event_ID %in% stack_sequence) %>%
                # , 
                # Strata == "Tree") %>%
  left_join(df_genus) %>%
  dplyr::group_by(!!as.name(input$stack_spgroup)) %>%     #either group by plant code or by a group of selected genuses????
  dplyr::summarize(tree_obs = n()) %>%
  ungroup() %>%
  top_n(7, tree_obs) %>%
  droplevels(.)

woodystacktop_species <- df_stacktop %>%
                        distinct(!!as.name(input$stack_spgroup)) %>%  # use !!as.name to refer to the column
                        pull(.)

woodystacktop_species <- as.character(c(as.character(woodystacktop_species), "Other"))

  } else {
    # input$stack_spgroup <- "Plant_Code" testing to make sure plant_code acutally works
    genus_group <- genus_grouping 
    # %>%
      # select(!!as.name(input$stack_spgroup), everything()) ### I actually think this doesn't do anything

    woodystacktop_species <- unique(genus_group[[input$stack_spgroup]])

    woodystacktop_species <- as.character(c(as.character(woodystacktop_species), "Other"))

    df_treefull %<>%
      full_join(genus_grouping) %>%
      dplyr::select(-Genus)

  }

# rv$df_treefull <- df_treefull

df_sptreefull <- df_treefull %>%
  dplyr::filter(Event_ID %in% stack_sequence) %>%
  left_join(df_genus) %>%
  dplyr::mutate(Subunit_Code = substr(Plot_Code, 1, 4),
                Plant_Code = as.factor(Plant_Code)) %>%
  dplyr::mutate(Plot_Genus = forcats::fct_other(.[[input$stack_spgroup]], #works for genus genus and genus group
                                                   keep = woodystacktop_species, ### this could be an input
                                                   other_level = 'Other')) %>%
  dplyr::mutate(Plot_Genus = as.factor(Plot_Genus)) %>% 
  dplyr::mutate(!!as.name(input$stack_usergroup) := case_when(
    Plot_Genus == "Other" ~ "Other", 
    TRUE ~ .[[input$stack_usergroup]])) %>%
  dplyr::group_by(Sample_Year, Strata,
                  !!as.name(input$stack_usergroup)) %>%
  dplyr::summarise(Count = sum(Count, na.rm = TRUE)) %>%
  ungroup() 

stack_expan <- df_sptreefull %>%
  dplyr::select(Sample_Year, Strata) %>%
  distinct() %>%
  dplyr::mutate(
    # Dynamically create a column based on input$map_usergroup
    !! input$stack_usergroup := "Other",  
    Count = 0  # Add 'Count' column with value 0
  )


df_sptreefull %<>%
  full_join(stack_expan) %>%
  dplyr::group_by(Strata, #Plot_Genus, Sample_Year
                  !!as.name(input$stack_usergroup)) %>%
  dplyr::summarise(Count = sum(Count)) %>%
  ungroup() 
  

col_sptreefull <- df_sptreefull %>%
  tidyr::pivot_wider(names_from = input$stack_usergroup, 
                     values_from = Count)

rv$col_sptreefull <- col_sptreefull

  columns_to_include <- col_sptreefull %>%
    dplyr::select(-Strata) %>% #Sample_Year, 
    
    dplyr::select(Other, everything()) %>%
    colnames()

  # rv$columns_to_include <- columns_to_include 

  color_palette <- jane[1:length(columns_to_include)]

  color_palette[length(color_palette)] <- "#333333"

  # rv$color_palette <- color_palette
  
  columns_to_include <- c(setdiff(columns_to_include, "Other"), "Other")


nn <- setNames(color_palette, columns_to_include)
 
colors <- columns_to_include

df_sptreefull[[input$stack_usergroup]] <- factor(df_sptreefull[[input$stack_usergroup]], levels = columns_to_include)

# Check the levels to confirm the order
levels(df_sptreefull[[input$stack_usergroup]])

page_height = 550

  # species_group_og <- input$stack_usergroup

    plot_tree <- df_sptreefull %>%
       ggplot2::ggplot(aes(x = Strata, 
                           y = Count, 
                           fill = !!as.name(input$stack_usergroup))) + 
       geom_bar(width = 0.45, 
                position = "fill", 
                stat = "identity") + 
       theme_clean() + 
       labs(x = "", y = "") + 
       ggtitle("") + 
       theme(plot.title = element_text(lineheight = 3, 
                                       face = "bold", 
                                       color = "black", 
                                       size = 12)) + 
      scale_fill_manual(values = nn[colors]) +
       scale_x_discrete(limits = positions) 
       
   rv$plotly_tree <-
 # if (x == 1 ) {
       ggplotly(plot_tree, height = page_height, width = 550) %>% #, height = page_height
  layout(margin = list(
    l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 40),
  legend = list(orientation = 'h',
                xanchor = "center",
                borderwidth = 0.5,
                x = 0.5,
                y = -0.25,
                title = "",
                # title = list(font = list(size = 12)),
                font = list(size = 11)),
  annotations = list(text = paste0("Relative Proportion of Woody Stem Size Classes within <br>", input$stack_userhabitat, " of ",input$stack_userunit), 
                     font = list(size = 13), 
                     showarrow = FALSE,
                     xref = 'paper', x = 0.75,
                     yref = 'paper', y = 1.1), 
  annotations = list(text = paste0("Number of Surveyed Plots:", sum(count(nplot)$freq), "<br>Total densities of genera in all plots of the selected spatial and habitat groups <br> (seedlings and saplings summed at 1 and 10 m2 quadrats; <br> trees summed at the 400m2 plot level)"), #added comma
                     font = list(size = 12), 
                     showarrow = FALSE,
                            xref = 'paper', x = 0.5,
                            yref = 'paper', y = -0.30)
  ) 
   
})
```

Relative Prop of Genera {data-orientation=rows}
========================================================================
### <font style="font-size: 20px"> Relative Proportion of Woody Species </font>

*<font size="3"> This graph shows the relative density of woody plant genera for a selected year, park, community group, and number of plots in this community group.* </font>
*<font size="3"> Each bar represents a different size class of woody plant - seedling, sapling, and tree.* </font>
*<font size="3"> The 8 genera with the highest density of trees are displayed, and with all other genera binned into an ‘Other’ category. *</font>

Inputs {.sidebar data-width=300}
-------------------------------------
```{r}
div(style = "margin-top: 10px; align-self: left; ",
   actionButton("button_UpdatePlots", "Update Plots")

   )
  
  div(style = "margin-top: 10px;", 
    
renderUI({   
selectInput(
  "stack_spatialunit",
  label = strong("Select Spatial Scale: "),
  choices = c("Network_Code", "Park_Code", "Subunit_Code") 
)
})
)
 


renderUI({ #needed bc reactive
  shiny::req(!is.null(input$stack_spatialunit), !is.null(all_events))
  
  selectInput(
    "stack_userunit",
    label = strong(paste0("Select Individual Unit of ", input$stack_spatialunit, ":" )),
    choices = unique(all_events[input$stack_spatialunit]) %>% pull(.) %>% sort()
  )

})



renderUI({
  shiny::req(!is.null(all_events))
  
  if ("Cycle" %in% names(all_events)) {
    conditionalPanel(
    condition = "(Cycle %in% names(all_events))",
    selectInput("stack_season", 
                label = strong("Select Temporal Grouping:"), 
                choices = c("Sample_Year", "Cycle") ))
    
    } else {
      selectInput("stack_season", 
                label = strong("Select Temporal Grouping:"), 
                choices = c("Sample_Year"), 
                selected = "Sample_Year")
      
      }
})


          renderUI({
      shiny::req(!is.null(all_events), !is.null(input$stack_spatialunit), !is.null(input$stack_userunit), !is.null(input$stack_season))
   
      yearchoice <- all_events %>%
        dplyr::filter(!!as.name(input$stack_spatialunit) == input$stack_userunit) %>%
        distinct(!!as.name(input$stack_season)) %>%
        pull(.)
      
      selectInput(
        "stack_year", 
        label = strong("Select", paste0(input$stack_season), ":"), 
        choices = sort(yearchoice),
        selected = min(as.numeric(as.character(yearchoice)), na.rm = TRUE)
        )
      })




renderUI({
  shiny::req(!is.null(broadgroup), !is.null(remove_habcolumns))
  
  habgroup <- names(broadgroup)[! names(broadgroup) %in% remove_habcolumns]
  
  selectInput(
  "stack_spatialhabitat", 
  label = strong("Select Habitat Group: "),
  choices = c("All", sort(habgroup))
  )

})

renderUI({
     shiny::req(!is.null(input$stack_spatialunit), !is.null(input$stack_userunit), !is.null(input$stack_season), !is.null(input$stack_year), !is.null(input$stack_spatialhabitat), !is.null(all_events))

  if (input$stack_spatialhabitat == "All") {
     selectInput(
    "stack_userhabitat",
    label = strong("Select Habitat Grouping: "),
    choices = c("All")
  )  } else {

  communitychoice <- all_events %>%
    dplyr::filter(!!as.name(input$stack_season) %in% input$stack_year,
                  !!as.name(input$stack_spatialunit) == input$stack_userunit) %>%
    distinct(!!as.name(input$stack_spatialhabitat)) %>%
    pull(.)

  selectInput(
    "stack_userhabitat",
    label = strong("Select Habitat Grouping: "),
    choices = c(sort(communitychoice))
  )
  }

})

   renderUI({
    if (!exists("genus_grouping") || is.null(genus_grouping)) {      # If `genus_grouping` exists and is not null
      
      selectInput(
        "stack_usergroup",
        label = strong("Select a species grouping:"),
        choices = "Genus",                    # Default value if null
        selected = "Genus"
      )

    } else {
      # If `genus_grouping` is null

      genuscols <- colnames(genus_grouping)  # Get the column names

      selectInput(
        "stack_usergroup",
        label = strong("Select a species grouping:"),
        choices = sort(genuscols),            # Provide the sorted column names
        selected = "Genus"
      )
    }
  })


    renderUI({
   shiny::req(!is.null(input$stack_usergroup))
      
      if (input$stack_usergroup == "Genus") {
      
      selectInput(
        "stack_spgroup",
        label = strong("Select a taxanomic grouping: "),
        choices = c("Genus"),
        selected = "Genus"
      ) } else {
    
         selectInput(
        "stack_spgroup",
        label = strong("Select a taxanomic grouping: "),
        choices = "Plant_Code",
        selected = "Plant_Code")
  }
})



```


Rows {data-height=650}
-----------------------------------------------------------------------
###
```{r}
output$plotly_tree <- renderPlotly({
  shiny::req(!is.null(rv$plotly_tree))
  rv$plotly_tree})

plotlyOutput("plotly_tree", height = "100%", width = "50%")
```

Rows {.tabset .tabset-fade data-height=250}
-----------------------------------------------------------------------
### Filtered Data
```{r}
output$woody_filteredtable <- renderReactable({
  shiny::req(!is.null(rv$col_sptreefull))

  reactable::reactable(rv$col_sptreefull,
                       fullWidth = TRUE,
                       compact = TRUE,
                       # resizeable = TRUE,
                       defaultColDef = colDef(vAlign = "center",
                                            headerVAlign = "bottom",
                                            align = "left",
                                            class = "group",
                                            minWidth = 70,
                                            headerClass = "header")

                       )
})

reactableOutput("woody_filteredtable", height = "40%")

# verticalLayout(plotlyOutput("plotly_tree"), reactableOutput("table_tree"))
```

### Raw Data
```{r}

output$woody_rawtable <- renderReactable({
  shiny::req(!is.null(df_treefull))
  reactable::reactable(df_treefull, 
                       fullWidth = TRUE, 
                       compact = TRUE, 
                       pagination = TRUE,
                       filterable = TRUE,
                       defaultColDef = colDef(
                         vAlign = "center",
                         headerVAlign = "bottom",
                         align = "left",
                         class = "group",
                         minWidth = 70,
                         headerClass = "header"
                         ))
  
})

reactableOutput("woody_rawtable", height = "40%")

```


```{css styles}
.border-left {
  border-left: 14px solid #000;
  font-size: 12px
}

.header { 
  border-bottom-color: #555;
  border-top-color: #555;
  font-size: 13px;
  font-weight: 600;
}

.group {
  font-size: 12px;
}

.reactable {
font-size: 12px; 
}

.cell {
  font-size: 12px;

}

.cellitalics {
  font-style: italic;
}

.sidenav { 
  overflow: scroll;  
  overflow-y: scroll;
  height: 3000px;
  width: 300px;
  position: fixed;
  z-index: 1;
  top: 0;
  left: 0;
  background-color: #dde6f0;
  padding-top: 80px;
  padding-right: 10px;
  padding-left: 10px;
}

.table {
  margin-left:250px;
}
```


