---
title: "WoodyMap_2424"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll 
    runtime:: shiny
---
```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

rm(list=ls())

#options(url.method = "wininet")
#options(repos="http://cran.revolutionanalytics.com")
#options(repos = c(CRAN = "https://cloud.r-project.org"))

### Load libraries -----
# Will automatically install any libraries it can't find
pkgs <- c("flexdashboard", 
              "shiny", 
              "knitr", 
              "odbc", # pull data from SQL server
              "leaflet", 
              "here",
              "plotly", 
              "tidyverse", 
              "plyr", 
              "sf",
              "readr",
              "magrittr",
              "bslib", 
              "ggplot2",
              "patchwork",
              "leaflet.extras", 
              "lubridate",
              "forcats",
              "httr", # use web services
              "rgdal", # to use readOGR
              "sp", # transform projections
              "purrr", # for applying functions to dplyr groups
              "dataMaid", # for data checks
              "shinyFiles", # for user to save files in specified location
              "RColorBrewer", # to display brewer palettes
              "shinyjs", # for easy functions that use JavaScript
              "stringr", # to detect text snippets
              "reactable",
              "reactablefmtr",
              "base", 
              "htmltools", 
              "ggthemes",
              "data.table", # for fast lag calcs
              "DT", # for interactive tables
              "cowplot", # to get legends from plots
              "crosstalk", # for SharedData
              "gridExtra", # for arranging plots and adding plot annotations (ggplotly can't do captions or subtitles)
              "RgoogleMaps", # for MaxZoom & MinZoom
              "leaflet.minicharts") # for pie charts in leaflet maps


installed_pkgs <- pkgs %in% installed.packages()
if (length(pkgs[!installed_pkgs]) > 0) install.packages(pkgs[!installed_pkgs],dep=TRUE) 
lapply(pkgs, library, character.only = TRUE)

invisible(lapply(pkgs, library, character.only = TRUE))

options(shiny.maxRequestSize=60*1024^2) #increase the file upload limit to 90MB.

rv <- reactiveValues(SeedlingSapling = NULL, SpeciesDiversity = NULL, Tree = NULL, CanopyCover = NULL, StandHeight = NULL, Genus = NULL, LatLong = NULL, Species_Cover = NULL, Cover_Class = NULL, Exotics = NULL, CWD = NULL, BroadGroup = NULL, CycleNumber = NULL)

temp_rv <- shiny::reactiveValues(
  df_mapwide = NULL, 
  columns_to_include = NULL,
  color_palette = NULL, 
  bc = NULL, 
  df_spdivbar = NULL, 
  divtable = NULL
)
```

```{r message = FALSE, results = FALSE, echo = FALSE}
#reading in csvs

trees <- read_csv(here::here("output", "CUPN_TreeBasics.csv")) #NEWNEW cycle tree basics
seedlingsapling <- read_csv(here::here("output", "CUPN_SeedlingSapling.csv")) #NEWNEW cycle seedling sapling
broadgroup <- read_csv(here::here("output", "CUPN_BroadGroup.csv")) #used to be broadgroup
# species_rich <- read_csv(here::here("Data_In","SpeciesDiversity_LongFormat_20230421.csv")) #waiting on new data from Tim
genus <- read_csv(here::here("output", "TaxaTable.csv"))
location <- read_csv(here::here("output", "Location_Table.csv")) #let's just call this LOCATION
canopycover <- read_csv(here::here("output", "CUPN_CanopyCover.csv"))
genus_group <- read_csv(here::here("output", "Genus_grouping.csv"))
events <- read_csv(here::here("output", "CUPN_EventTable2.csv"))
shapefile <- st_read(here::here('./cupn_shapefile/CUPN.shp'))
  
mp_compboundary <- st_transform(shapefile, crs = 4326)

```

```{r functions}
### Functions-----

#rounding function 
#stick to a certain function naming rule
round_df <- function(x, digits) {
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

options(scipen=999)

#keeping only first letter of character
makeInitials <- function(charVec) {
  make.unique(vapply(strsplit(toupper(charVec), " "), 
                     function(x) paste(substr(x, 1, 1), collapse = ""), 
                     vector("character", 1L)))
}

#color palettes
Okabe_Ito <- c("#E69F00", "#56B4E9", "#009E73", '#CC6677',"#F0E442", "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",'#DDDDDD', '#EE6678', '#99DDFF', 
               '#BBCC33', '#332288', '#882255', '#FFAABB')

okabe_ito <- c( "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",  '#CC6677', '#BBCC33', '#99DDFF', 
                '#332288', '#882255', '#FFAABB', "#E69F00", "#56B4E9", "#009E73", "#F0E442")

viridis <- c("#fde725", "#5ec962", "#21918c","#3b528b","#440154")

jane <- c('#a5cee2', '#1f78b4', '#b2df8a', '#e7298b', '#33a02b', '#997dd4', '#000000', '#fc9a99','#e21a1c', '#fdbe6f', '#ff7f00', '#9c9c9c', '#cab2d6', '#6a3d9a', '#feff99', '#b15929')

# function to group by a plot, year and find the count of n
makefun <- function(data) {
  data %>% 
  dplyr::group_by(Plot_Code, Year) %>%
  dplyr::summarize(n())
  
}
##### css functions
integer_columns <- function(maxWidth = 60, ...) {
  colDef(maxWidth = maxWidth, align = "center",...)
}

with_tooltip <- function(value, tooltip) {
  tags$abbr(style = "text-decoration: underline; text-decoration-style: dotted; cursor: help", title = tooltip, value)
}

# lists for organizing column orders
positions <- c("Tree", "Sapling", "Seedling")

col_group <- c("Plot_Code", "Plant_Code", "Start_Date", "Sample_Year", "Event_ID")

#Needs to get ride of Network, Park, and Subunit, Change Start_Date to Sample Date?
common_columns <- c("Network_Code", "Park_Code", "Subunit_Code", "Plot_Code", "Start_Date", "Event_Type_Name", "Year") 
```

```{r}
func_processdata <- function(df, growth_form) {
  df %>%
    dplyr::mutate(Start_Date = as.Date(lubridate::mdy_hm(Start_Date)),
                  Sample_Year = as.factor(Sample_Year),
                  Growth_Form = growth_form)
}

df_genus <- genus %>% 
  dplyr::select(Plant_Code, Genus) 

df_events <- func_processdata(events, NA)

df_events %<>%
  dplyr::mutate(Subunit_Code = substr(Plot_Code, 1, 4))

df_trees <- func_processdata(trees, "Tree") %>%
  dplyr::filter(Status_Name == "Live Tree") %>%
  dplyr::mutate(BA_ha = ((pi * DBH^2) / 40000) / 0.04)

df_seedsap <- func_processdata(seedlingsapling, NA)

 # new code for woody map _flex24
location %<>%
    dplyr::select(Park_Code, Subunit_Code, Plot_Code, Latitude, Longitude)


df_treedivsum <- df_trees %>% #----------Summing basal area per growth form, year, plot, and subunit 
  dplyr::group_by(Plot_Code, Start_Date, Event_ID, Sample_Year, Growth_Form) %>%
  dplyr::summarise(Sum = sum(BA_ha)) %>%
  tidyr::pivot_longer(cols = Sum, 
                      names_to = "Plant_Code", 
                      values_to = "Count")
  # tidyr::pivot_longer(cols = Sum, 
  #                     names_to = "Genus", 
  #                     values_to = "Count")   old code when GENUS was still included in the input data
  # is there a better way? Should we keep df_treediv and df_treedivsum separate?

df_treediv <- df_trees %>% #----------finding raw count of live trees per growth form, year, plot, and subunit - are we not taking genus into account?? just raw numbers?? for us just plant_code which DOOESSS reduce the amount of observatiosn not as much as if by genus hmmmmmmmmmmmmmmmm
  dplyr::group_by(Plot_Code, Start_Date, Event_ID, Sample_Year, Plant_Code, Growth_Form) %>%
  dplyr::summarize(Count = n()) %>%
  ungroup() %>%
  full_join(df_treedivsum)



func_seedsap <- function(df, form_col, total_col) {
  df %>%
    replace(is.na(.), 0) %>%
    dplyr::group_by(Plot_Code, Start_Date, Event_ID, Sample_Year, Plant_Code, Growth_Form = form_col) %>%
    dplyr::summarise(Count = sum({{total_col}}, na.rm = TRUE)) %>%
    ungroup()
}

df_mapsapdiv <- func_seedsap(df_seedsap %>% dplyr::mutate(Growth_Form = "Sapling"), "Sapling", Sapling_Total)

df_mapsapsum <- df_seedsap %>%
  dplyr::mutate(
    Growth_Form = "Sapling",
    Sapling01_BA =  (0.00007854 * (0.5)^2 ) * Sapling_0_1_DBH,
    Sapling12h_BA = (0.00007854 * (1.75)^2 ) * Sapling_1_2half_DBH,
    Sapling2h5_BA = (0.00007854 * (3.25)^2 ) * Sapling_2half_5_DBH ,
    Sapling510_BA = (0.00007854 * (7.5)^2 ) * Sapling_5_10_DBH
  ) %>%
  dplyr::group_by(Plot_Code, Start_Date, Event_ID, Sample_Year, Growth_Form) %>%
  dplyr::summarise(
    Sum = sum(Sapling01_BA, Sapling12h_BA, Sapling2h5_BA, Sapling510_BA, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  tidyr::pivot_longer(
    cols = Sum,
    names_to = "Plant_Code",
    values_to = "Count"
  )

df_sapdiv <- dplyr::full_join(df_mapsapdiv, df_mapsapsum) #-------joining count and basal area calculations for saplings

df_mapseeddiv <- func_seedsap(df_seedsap %>% dplyr::mutate(Growth_Form = "Seedling"), "Seedling", Seedling_Total)

df_mapseedsum <- df_mapsapsum %>%
  dplyr::mutate(Growth_Form = "Seedling", 
                Count = 50) # so much easier lol

df_seeddiv <- dplyr::full_join(df_mapseeddiv, df_mapseedsum) 


df_spdiv <-  Reduce(function (...) { merge(..., all = TRUE) },  #full join idk why I can't just do a regular left join....
                        list(df_treediv, df_sapdiv, df_seeddiv))
#### end of code within the flexdashboard

genus_grouping <-  if (!exists("genus_group")) {
  genus_grouping <- NULL
  } else { 
  genus_grouping <- genus_group
  }
```


```{r TRYING TO SEE FOR PLANT CODE}
# input <- list()
# input$size_class = "Sapling"
# # input$map_year <- "2017"
# input$map_subunit <- "COWP" #check
# input$map_spgroup <- "Plant_Code" # options are Genus and PLant Code
# input$map_usergroup <- "Group22" # options are Genus, user group x y and z
# input$map_season <- "Cycle"
# input$map_year <- "2"

observeEvent(eventExpr = input$button_UpdateMap, {
  shiny::req(!is.null(df_trees), !is.null(df_spdiv),  !is.null(input$map_subunit), !is.null(input$map_year), !is.null(input$size_class), !is.null(input$map_spgroup), !is.null(input$map_usergroup))
  
   withProgress(message = "Just a moment", detail = "Generating woody species map...", value = 0, { 
#### OBSERVE EVENT

# saveRDS(isolate(reactiveValuesToList(input)), paste0("bc_input.RDS"))
# saveRDS(isolate(reactiveValuesToList(rv)), paste0("bc_rv.RDS"))

     
 
     
map_sequence <- df_events %>%
  dplyr::filter(Subunit_Code == input$map_subunit) %>%
  dplyr::filter(!!as.name(input$map_season) == input$map_year) %>%
  pull(Event_ID)

rv$map_sequence <- map_sequence
     
     
     
     
     
# woodymptop_species <- 
  if (input$map_spgroup == "Genus" & input$map_usergroup == "Genus") {
#################### THIS WOULD HAVE TO BE A POTENTIAL CHANGE TO THIS PAGE.....EITHER THIS OR WOULD HAVE TO TAKE THE 
df_treesunits <- df_trees %>%
  dplyr::filter(Event_ID %in% map_sequence) %>%
  # dplyr::filter(str_detect(Plot_Code, input$map_subunit),
  #               !!as.name(input$map_season) %in% input$map_year) %>%
  left_join(df_genus) %>%
  dplyr::group_by(!!as.name(input$map_spgroup)) %>%     # I mean this HAS TO BE GENUS DON'T NEED THE INPUTeither group by plant code or by a group of selected genuses????
  dplyr::summarize(tree_obs = n()) %>%
  ungroup() %>%
  top_n(7, tree_obs) %>%
  droplevels(.)


woodymptop_species <- df_treesunits %>%
                        distinct(!!as.name(input$map_spgroup)) %>%  # use !!as.name to refer to the column
                        pull()

woodymptop_species <- as.character(c(as.character(woodymptop_species), "Other", "Sum"))
  } else {
    
    genus_group <- genus_grouping %>%
      select(!!as.name(input$map_spgroup), everything())

    woodymptop_species <- unique(genus_group[[input$map_spgroup]])

    woodymptop_species <- as.character(c(as.character(woodymptop_species), "Other", "Sum"))

    df_spdiv <- df_spdiv %>%
      full_join(genus_grouping) %>%
      dplyr::select(-Genus)

  }

spdiv <- df_spdiv %>%
  left_join(df_genus, by = "Plant_Code") %>%
  dplyr::mutate(Subunit_Code = substr(Plot_Code, 1, 4),
                Plant_Code = as.factor(Plant_Code)) %>%
  dplyr::mutate(Plot_Genus = forcats::fct_other(.[[input$map_spgroup]], #works for genus genus and genus group
                                                   keep = woodymptop_species, ### this could be an input
                                                   other_level = 'Other')) %>%
  dplyr::mutate(Plot_Genus = as.character(Plot_Genus)) %>%
  dplyr::mutate(Genus = case_when(
    Plant_Code == "Sum" ~ "Sum",
    TRUE ~ Genus)) %>%
  dplyr::mutate(Plot_Genus = case_when(
    Plant_Code == "Sum" ~ "Sum",
    TRUE ~ Plot_Genus)
  ) %>%
  dplyr::mutate(Plot_Genus = as.factor(Plot_Genus)) %>% 
  dplyr::mutate(!!as.name(input$map_usergroup) := case_when(
    Plot_Genus == "Sum" ~ "Sum", 
    Plot_Genus == "Other" ~ "Other", 
    TRUE ~ .[[input$map_usergroup]])) %>%
  dplyr::group_by(Subunit_Code, Event_ID, Plot_Code, Sample_Year, Growth_Form, #Plot_Genus,
                  !!as.name(input$map_usergroup)) %>%
  dplyr::summarise(Count = sum(Count)) %>%
  ungroup() 

mp_expan <- spdiv %>%
  dplyr::select(Subunit_Code, Event_ID, Plot_Code, Sample_Year, Growth_Form) %>%
  distinct() %>%
  dplyr::mutate(
    # Dynamically create a column based on input$map_usergroup
    !! input$map_usergroup := "Other",  
    Count = 0  # Add 'Count' column with value 0
  )

spdiv %<>%
  full_join(mp_expan) %>%
  dplyr::group_by(Subunit_Code, Event_ID, Plot_Code, Sample_Year, Growth_Form, #Plot_Genus,
                  !!as.name(input$map_usergroup)) %>%
  dplyr::summarise(Count = sum(Count)) %>%
  ungroup() 
  
# rv$spcomp <- spcomp # save spdiv is the equivalent into a reactive format
# rv$spdiv <- spdiv

df_mapwide <- spdiv %>%
  tidyr::pivot_wider(
    names_from = input$map_usergroup, #input$map_usergroup, #Plot_Genus,
    values_from = Count) %>%
  dplyr::select(Subunit_Code, Event_ID, Plot_Code, Sample_Year, Growth_Form, sort(setdiff(tidyselect::peek_vars(), "Other")), Other)  # dplyr::select(-Other, Subunit_Code, Plot_Code, Sample_Year, sort(tidyselect::peek_vars())) # I'm worried about the select -Other

rv$df_mapwide <- df_mapwide 

df_mapspdiv  <- df_mapwide %>%
  dplyr::filter(Growth_Form == input$size_class)


df_maplocation <- location  %>% 
  dplyr::select(-Park_Code) %>% #for some reason people want park code
  dplyr::mutate(PlotNum = substr(Plot_Code, 5, 10)) #------ PlotNum doesn't work for all networks

df_treedivmap <- left_join(df_mapspdiv, df_maplocation)

# rv$df_treedivtbl <- df_treedivmap %>%  calls to a reactive value
df_treedivtbl <- df_treedivmap %>%
  dplyr::select(Subunit_Code, Event_ID, Plot_Code, PlotNum, Sample_Year, Sum, everything())




df_treedivmap %<>%
  dplyr::filter(!is.na(Latitude)) %>%
  dplyr::filter(!is.na(Longitude)) %>%
  replace(is.na(.), 0) %>%
  dplyr::filter(Event_ID %in% map_sequence) %>%
  # filter(Sample_Year %in% input$map_year) %>%
  dplyr::select(sort(names(.))) %>%
  dplyr::select(-Other, everything()) #new code to order genus alphabetically doesn't do it,  why do I want this alphabetically???


park_zoom <- location %>%
  dplyr::filter(Subunit_Code == input$map_subunit)

bc = leaflet::leaflet(data = mp_compboundary) %>%
  addTiles() %>%
  addPolygons(data = mp_compboundary, color = ~ "black")

okabe_ito <- c("#0072B2", "#D55E00", "#009E73", '#99DDFF', 
                '#332288', '#882255', '#FFAABB', "#F0E442")

columns_to_include <- df_treedivmap %>%
  dplyr::select(-c(Subunit_Code, Event_ID, Growth_Form, Plot_Code, PlotNum, Sample_Year, Latitude, Longitude, Sum)) %>%
  # -Other, sort(tidyselect::peak(vars())))
  dplyr::select(Other, everything()) %>%
  colnames()

rv$columns_to_include <- columns_to_include 

color_palette <- okabe_ito[1:length(columns_to_include)]

color_palette[length(color_palette)] <- "#333333"

rv$color_palette <- color_palette
# color_palette

bc <- bc %>%
    addCircleMarkers(data = df_treedivmap,
               lng = ~Longitude,
               lat = ~Latitude,
               labelOptions = labelOptions(noHide = F),
               layerId = ~Plot_Code,
               group = "Markers"
    ) %>%
    addMinicharts(df_treedivmap$Longitude, #########CHANGE DATA
                  df_treedivmap$Latitude,
                chartdata = dplyr::select(df_treedivmap, -c(Subunit_Code, Event_ID, Growth_Form, Plot_Code, PlotNum, Sample_Year, Latitude, Longitude, Sum)),
                # , -Other, sort(tidyselect::peak(vars()))), #trying to order alphabetically
    type = "pie",
    width = 45,#sqrt(df_treedivmap$Sum) * 200, #### this might change totally
    col = color_palette, #Okabe_Ito,
    showLabels = F,
    ) %>%
  addLabelOnlyMarkers(df_maplocation$Longitude,
                      df_maplocation$Latitude,
                      label =  df_maplocation$PlotNum,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#000000", 'fontSize'="18px"))) %>%
    addScaleBar(position = "bottomright") %>%
  fitBounds(min(park_zoom$Longitude), min(park_zoom$Latitude), max(park_zoom$Longitude), max(park_zoom$Latitude)) %>%
    addLayersControl(
      overlayGroups = c("Markers"), 
      options = layersControlOptions(collapsed = FALSE)

    )

cat("Line4")

saveRDS(isolate(reactiveValuesToList(input)), paste0("bc_input.RDS"))
saveRDS(isolate(reactiveValuesToList(rv)), paste0("bc_rv.RDS"))

 rv$bc <- bc

 

# 
})
})
  
click_marker <- eventReactive(input$leaflet_marker_click, {
  # withProgress(message = "Just a moment", detail = "creating proptional stacked barchart...", value = 0, { 


 site <- input$leaflet_marker_click

 return(site$id)
 
cat("line1453")
})

# df_mapwide instead of df_treedivmap same wide format thoughhhh
# chardata_long <- df_treedivmap
renderUI({
  shiny::req(!is.null(click_marker), !is.null(rv$df_mapwide), !is.null(rv$color_palette), !is.null(rv$columns_to_include), !is.null(rv$map_sequence), !is.null(input$map_season))
  
chartdata_long <- rv$df_mapwide %>%
   dplyr::filter(Plot_Code == click_marker(), #"COWP013", ########## SHOULD BE click_marker(), ,#
                Event_ID %in% rv$map_sequence) %>%
  dplyr::select(Plot_Code, Event_ID, Sample_Year, Growth_Form, all_of(rv$columns_to_include)) %>%
  tidyr::pivot_longer(cols = all_of(rv$columns_to_include), 
                      names_to = "Plot_Genus", 
                      values_to = "Count") %>%
  replace(is.na(.), 0)


columns_to_include2 <- c(setdiff(rv$columns_to_include, "Other"), "Other")

# Print the reordered vector to confirm
print(columns_to_include2)

# rv$color_palette

nn <- setNames(rv$color_palette, columns_to_include2)
 
colors <- columns_to_include2
  
# sort(unique(chartdata_long$Plot_Genus))
  
  
chartdata_long$Plot_Genus <- factor(chartdata_long$Plot_Genus, levels = columns_to_include2)

# Check the levels to confirm the order
levels(chartdata_long$Plot_Genus)
  
rv$df_spdivbar <- chartdata_long %>%
  dplyr::filter(Plot_Code == click_marker(), #"COWP013", ########## SHOULD BE click_marker(), ,#
                Event_ID %in% rv$map_sequence) %>%
                # Sample_Year %in% input$map_year) %>%
  ggplot(aes(x = Growth_Form, y = Count, fill = Plot_Genus)) +
  geom_bar(width = 0.45, 
           position = "fill",
           stat = "identity") +
  theme_clean() +
  # labs(x = "", y = "Proportion of genera", title = paste0("", input$size_class, ", ", input$map_year, ", ", click_marker())) + # paste0("", input$prop_year, ", ", input$Individual_Unit, ", ", input$Association))
  scale_x_discrete(limits = positions) +
    scale_fill_manual(values = nn[colors],
#scale_fill_manual(values = okabepalette[unique(rv$spcomp$Plot_Genus)],
                      drop = TRUE) 
})


renderUI({
  shiny::req(!is.null(rv$df_mapwide), !is.null(click_marker), !is.null(input$map_subunit), !is.null(rv$map_sequence))

  # rv$comptable <- rv$df_treedivtbl %>%
divtable <- rv$df_mapwide %>% #df_treedivtbl %>%
    dplyr::select(-Sum) %>%
    dplyr::filter(
      # Plot_Code == "COWP013",
      Event_ID %in% rv$map_sequence, 
      Plot_Code == click_marker()
      )
      
      # ,, !is.null(input$map_season), !is.null(input$map_year)
      # !!as.name(input$map_season) %in% input$map_year)


  cat("Line44")

  rv$divtable <- divtable

  cat("Line44 divtable structure: ", str(rv$divtable))

})

```



Maps
=======================================================================
### <font style="font-size: 20px"> Mapped Proportion of Woody Species </font>

*<font size="3"> This map shows pie charts of genera for each plot containing data in a given year and park subunit.  * </font>
*<font size="3"> De-select "marker' and select "marker" again to be able to click on a plot and see the corresponding proportional stacked bar chart. In order to see the raw numbers on the plot, unselect "marker" and click on the pie chart itself. * </font>
*<font size="3"> The top 8 genera are shown for TREES (in a given year and park subunit) in each bar chart and other genera are binned as "other". *</font>
*<font size="3"> Seedling, sapling, and tree densities are NOT yet calculated at the count/ha scale (do you want the raw counts per plot or do you want them converted to count/ha?)----- ". *</font>

####

```{r}
#---------Needs to change to incorportate Cycle/Year, Subunit/Park, and Different Genus Groupings

div(
  style = "display: flex; flex-wrap: wrap;",
  
div(style = "margin-top: 10px; margin-right: 30px; align-self: center; ",
    actionButton("button_UpdateMap", "Update Map")
   ), 
  
  div(style = "margin-top: 10px;", 
    
    renderUI({
    shiny::req(!is.null(location))
    
  selectInput(
    "map_subunit",
    label = strong("Select a Unit: "),
    choices = sort(unique(location$Subunit_Code)),
    selected = switch(is.null(input$map_subunit)+1, input$map_subunit, "BIRT")
    )
})
),


div(style = "margin-top: 10px;", 
    
    renderUI({
      shiny::req(!is.null(df_events))
      if ("Cycle" %in% names(df_events)) {
        conditionalPanel(
    condition = "(Cycle %in% names(df_trees))",
    selectInput("map_season", 
                label = strong("Select Temporal Grouping:"), 
                choices = c("Sample_Year", "Cycle") ))
    
    } else {
      selectInput("map_season", 
                label = strong("Select Temporal Grouping:"), 
                choices = c("Sample_Year"), 
                selected = "sample_Year")
      
      }
    })
    ),

div(style = "margin-top: 10px;", 
    renderUI({
      shiny::req(!is.null(df_events), !is.null(input$map_subunit), !is.null(input$map_season))
   
      yearchoice <- df_events %>%
        dplyr::filter(Subunit_Code == input$map_subunit) %>%
        distinct(!!as.name(input$map_season)) %>%
        pull(.)
      
      selectInput(
        "map_year", 
        label = strong("Select", paste0(input$map_season), ":"), 
        choices = sort(yearchoice),
        selected = min(as.numeric(as.character(yearchoice)), na.rm = TRUE)
        )
      })

),
   div(style = "margin-top: 10px;", 
       renderUI({ 
         shiny::req(!is.null(df_trees))
         selectInput(
           "size_class", 
           label = strong("Select a size class: "), 
           choices = c("Tree", "Sapling", "Seedling"), 
           selected = "Tree"
           )
         })
       ), 

div(style = "margin-top: 10px;",
    renderUI({
  # shiny::req(!is.null(df_trees))
      selectInput(
        "map_spgroup",
        label = strong("Select a taxanomic grouping: "),
        choices = c("Genus", "Plant_Code"),
        selected = "Genus"
  )
})
),

div(style = "margin-top: 10px;",
  renderUI({
    if (!exists("genus_grouping") || is.null(genus_grouping)) {      # If `genus_grouping` exists and is not null
      
      selectInput(
        "map_usergroup",
        label = strong("Select a species grouping:"),
        choices = "Genus",                    # Default value if null
        selected = "Genus"
      )

    } else {
      # If `genus_grouping` is null

      genuscols <- colnames(genus_grouping)  # Get the column names

      selectInput(
        "map_usergroup",
        label = strong("Select a species grouping:"),
        choices = sort(genuscols),            # Provide the sorted column names
        selected = "Genus"
      )
    }
  })
)
)



```


Rows
-----------------------------------------------------------------------
###
```{r CUPN map}
output$leaflet <- renderLeaflet({
  shiny::req(!is.null(rv$bc)) 
  rv$bc
  })

leafletOutput("leaflet", height = "95vh")

```

###

```{r}

output$map_tree <- renderPlot({
  shiny::req(!is.null(rv$df_spdivbar))
  
  rv$df_spdivbar})

plotOutput("map_tree")
```


Rows {data-height=250}
-----------------------------------------------------------------------

```{r}
output$maptable <- renderReactable({
  shiny::req(!is.null(rv$divtable))


  reactable::reactable(rv$divtable,
                     pagination = FALSE,
                     highlight = TRUE,
                     fullWidth = TRUE,
                     filterable = TRUE,
                     resizable = T,
                     compact = TRUE,
                      defaultColDef = colDef(vAlign = "center",
                                            headerVAlign = "bottom",
                                            align = "left",
                                            class = "group",
                                            headerClass = "header",
                                            minWidth = 100,
                                            headerStyle = list(fontWeight = 500)
                                            ))
})

reactableOutput("maptable")
```


```{css styles}

.border-left {
  border-left: 14px solid #000;
  font-size: 12px
}

.header { 
  border-bottom-color: #555;
  border-top-color: #555;
  font-size: 13px;
  font-weight: 600;
}

.group {
  font-size: 12px;
}

.reactable {
font-size: 12px; 
}

.cell {
  font-size: 12px;

}

.cellitalics {
  font-style: italic;
}
```

